DRAFT Addition re Other Packages

### 2024-10-03 scratch/JSS-submission/Revision-1/Fox-Monette-cv-package.Rmd
fix typos in JSS paper

The \code{"function"} method for \code{cv()} cross-validates a model-specification process in a general manner. Functions for four such model-specification processes are included in the package: \code{selectStepAIC()}, based on the \code{stepAIC()} function in the \pkg{MASS} package [@VenablesRipley:2002], performs stepwise predictor selection for regression models; \code{selectTrans()}, based on the \code{powerTransform()} function in the \pkg{car} package, transforms predictors and the response in a regression model towards normality; \code{selectTransAndStepAIC()}---the use of which we illustrate in the current section---performs both of these procedures sequentially; and \code{selectModelList()}---also illustrated in the current section---uses CV both to select one of several competing models, and then, recursively, to estimate prediction error for the selected model, a process that we term "meta cross-validation."[^adding-model-selection]

@@

The \code{"function"} method for \code{cv()} allows us to cross-validate the whole model-selection procedure. The first argument to \code{cv()}---here \code{selectTransAndStepAIC}---is a model-selection function capable of refitting the model with a fold omitted and returning a CV criterion:
```{r Auto-transform-and-select}
num.predictors
cvs <- cv(selectTransStepAIC, data = Auto, seed = 76692, 
          working.model = m.auto, predictors = num.predictors,
          response = "mpg", AIC = FALSE)
summary(cvs)
```

@@

```{r compare-rsample-cv, cache=TRUE}
set.seed(53437)
print(microbenchmark::microbenchmark(
  cv.hatvalues = cv(mod.attrition, k = "loo", criterion = BayesRule,
                    method = "hatvalues"),
  cv.wood = cv(mod.attrition, k = "loo", criterion = BayesRule,
               method = "Woodbury"),
  cv.exact = cv(mod.attrition, k = "loo", criterion = BayesRule),
  direct = {
    n <- nrow(attrition)
    yhat <- numeric(n)
    for (i in 1:n){
      m <- update(mod.attrition, data = attrition[-i, ])
      yhat[i] <- predict(m, newdata = attrition[i, ], type = "response")
    }
    mean(((attrition$Attrition == "Yes") - round(yhat)) ^ 2)
  },
  rsample = {
    rs_obj$results <- map(rs_obj$splits, holdout_results, mod_form)
    rs_obj$accuracy <- map_dbl(rs_obj$results, 
                               function(x) mean(x$correct))
  },
  caret = train(x = attrition[, c("JobSatisfaction", "Gender",
                                  "MonthlyIncome")],
              y = attrition$Attrition,
              method = "glm", 
              trControl = trainControl(method = "LOOCV")),
  times = 10, unit = "relative"), signif = 3)
```
Computing time for \pkg{rsample} and \pkg{caret} for this problem is similar to direct computation of LOO CV and to \code{cv()} with \code{method="exact"}, but almost two orders of magnitude slower than \code{cv()} with \code{method="Woodbury"}, and more than three orders of magnitude slower then \code{cv()} with \code{method="hatvalues"}.

>>>>

The \code{"function"} method for \code{cv()} cross-validates a model-specification process in a general manner. Functions for four such model-specification processes are included in the package: \code{selectStepAIC()}, based on the \code{stepAIC()} function in the \pkg{MASS} package [@VenablesRipley:2002], performs stepwise predictor selection for regression models; \code{selectTrans()}, based on the \code{powerTransform()} function in the \pkg{car} package, transforms predictors and the response in a regression model towards normality; \code{selectTransStepAIC()}---the use of which we illustrate in the current section---performs both of these procedures sequentially; and \code{selectModelList()}---also illustrated in the current section---uses CV both to select one of several competing models, and then, recursively, to estimate prediction error for the selected model, a process that we term "meta cross-validation."[^adding-model-selection]

@@

The \code{"function"} method for \code{cv()} allows us to cross-validate the whole model-selection procedure. The first argument to \code{cv()}---here \code{selectTransStepAIC}---is a model-selection function capable of refitting the model with a fold omitted and returning a CV criterion:
```{r Auto-transform-and-select}
num.predictors
cvs <- cv(selectTransStepAIC, data = Auto, seed = 76692, 
          working.model = m.auto, predictors = num.predictors,
          response = "mpg", AIC = FALSE)
summary(cvs)
```

@@

```{r compare-rsample-cv, cache=TRUE}
set.seed(53437)
print(microbenchmark::microbenchmark(
  cv.hatvalues = cv(mod.attrition, k = "loo", criterion = BayesRule,
                    method = "hatvalues"),
  cv.wood = cv(mod.attrition, k = "loo", criterion = BayesRule,
               method = "Woodbury"),
  cv.exact = cv(mod.attrition, k = "loo", criterion = BayesRule),
  direct = {
    n <- nrow(attrition)
    yhat <- numeric(n)
    for (i in 1:n){
      m <- update(mod.attrition, data = attrition[-i, ])
      yhat[i] <- predict(m, newdata = attrition[i, ], type = "response")
    }
    mean(((attrition$Attrition == "Yes") - round(yhat)) ^ 2)
  },
  rsample = {
    rs_obj$results <- map(rs_obj$splits, holdout_results, mod_form)
    rs_obj$accuracy <- map_dbl(rs_obj$results, 
                               function(x) mean(x$correct))
  },
  caret = train(x = attrition[, c("JobSatisfaction", "Gender",
                                  "MonthlyIncome")],
              y = attrition$Attrition,
              method = "glm", 
              trControl = trainControl(method = "LOOCV")),
  times = 10, unit = "relative"), signif = 3)
```
Computing time for \pkg{rsample} and \pkg{caret} for this problem is similar to direct computation of LOO CV and to \code{cv()} with \code{method="exact"}, but almost two orders of magnitude slower than \code{cv()} with \code{method="Woodbury"}, and more than three orders of magnitude slower than \code{cv()} with \code{method="hatvalues"}.
